Stateless Model Checking with Data-Race Preemption Points

### 2015-11-03 pldi-16/intro.tex
add structural text

>>>>

The remainder of the paper is organized as follows.
\sect{\ref{sec:design}} discusses the background and design of Iterative Deepening,
\sect{\ref{sec:implementation}} explains \quicksand's approach to implementing it,
\sect{\ref{sec:eval}} presents our evaluation,
\sect{\ref{sec:future}} discusses limitations and future work,
\sect{\ref{sec:related}} surveys the related work,
and \sect{\ref{sec:conclusion}} concludes.
